---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "sophia-yi"
date: "25 September"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

```{r}
library(magrittr)     # the pipe
library(tidyverse)    # for data wrangling + visualization
library(tidymodels)   # for modeling
library(gt)           # for making display tables
library(gtExtras)     # helper functions for beautiful tables
library(DataExplorer) #
```

```{r}
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

```         
```

## Exercises

### Exercise 1

The `the_tate` dataset has 3336 unique artists who worked from 1545 to 2012. The works were acquired between the years1823 and 2013.

```{r}
the_tate |> dplyr::summarise(
  artist=length(unique(artist)),
  min_year=min(year,na.rm = TRUE),
  max_year=max(year,na.rm = TRUE),
    min_acqyear=min(acquisitionYear,na.rm = TRUE),
  max_acqyear=max(acquisitionYear,na.rm = TRUE),
  
)
```

```{r}
the_tate |> DataExplorer::introduce()
```

```{r}
the_tate |> DataExplorer::plot_missing()
```

### Exercise 2

How number of works with missing dates is \_2583\_.

The number of artists whose works have missing dates is \_461\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_MAR\_\_\_.

```{r}
the_tate |> dplyr::filter(is.na(year)) |> dplyr::distinct(title)
```

```{r}
the_tate |> dplyr::filter(is.na(year)) |> dplyr::distinct(artist)

```

```{r}
the_tate |> dplyr::filter(is.na(year))

#table(qaz$artist) |> tibble::tibble()
```

### Exercise 3

The artist with the most works in the Tate collection is \_Turner\_\_.

The artist with the tenth-most works in the Tate collection is \_Warhol\_\_.

```{r}
the_tate |> dplyr::group_by(artist) |>
dplyr::mutate(n=dplyr::n()) |>
  dplyr::select(artist,n) |> 
  dplyr::arrange(desc(n)) |>
  dplyr::distinct() |> 
  dplyr::ungroup() |> 
  dplyr::slice(c(1,10))
```

### Exercise 4

The artist with the greatest number of works in the Tate collection represent \_56.91970\_\_% of the total

```{r}
the_tate %>%
  dplyr::group_by(artist) %>%
  dplyr::mutate(works_count = dplyr::n()) %>%
  dplyr::select(artist, works_count) %>%
  dplyr::arrange(desc(works_count)) %>%
  dplyr::distinct() %>%
  dplyr::ungroup() %>%
  dplyr::mutate(
    total = sum(works_count),
    pct = works_count / total
  )
```

### Exercise 5

There are \_\_ duplicate artist-title pairs

```{r}

```

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
